\section{General conclusion}
\label{sec:conclusion}

This traineeship has been a very rich experience, for many reasons that have been detailed in the previous sections and that are summarized here in the general conclusion.

Technically, it brought me a lot of knowledge in a discipline that I had not experienced before: web development, and more specifically single-page applications. I have improved my skills in languages such as JavaScript, HTML and SCSS, and understood the concepts of frontend and backend. I learned the main good practices and principles for writing clean, understandable, maintainable code, and got to use some modern frameworks and libraries (ReactJS, Redux, GraphQL and more). This increased my curiosity about new technologies, and I got the chance to attend some very interesting conferences about them.

Moreover, I now know better how to use Github as a communication tool for technical issues, and how to deal with local branches, pull requests and multi-environmental development. Plus, I discovered the concept of feature flag, an insurance that critical changes will not affect the website before being completely finalized and tested.

Being part of a small team made me realize the importance of communication and collaboration in project management. I often worked with the designer and the community manager, which was also the occasion to learn more about their job and skillset. And since Konnektid is currently trying to prove their business model as a market place, I discovered the techniques that you can use to do so: web analytics, marketing tools, etc.

From the company point of view, I believe that I produced a lot of value in terms of new features and improvements in the web application. I mostly worked on frontend tasks, and was quickly able to deliver interfaces and components with good quality code and intelligent structure. But I was also able to work on other assignments, involving different technologies and sometimes backend problematics. I learned how to be independent and was able to decide by myself which task to start next, depending on the month's objectives for Konnektid. I was also involved in brainstorming sessions and meetings where my opinion and ideas were truly appreciated.

As a conclusion, the most valuable asset for me was to deal with such a huge variety of tasks, from building interfaces to implementing analytics or creating wireframes. It really made me think about what I like, and what I want to do after the internship.